A ``Dream'' Interface Design

### 2014-11-24 dream-design/dream-design.tex
add wireframe

In this investigation, I propose a ``dream'' interface design for touchscreen mobile devices that provides a significant amount of tactile feedback. This feedback is designed in a way that can be helpful for individuals with and without visual impairments alike. This design was developed with the usability metrics of learnability, efficiency, and errors in mind.

This design makes use of technology that is currently being created by Tactus, a company in Fremont California \cite{Tactus}. Tactus brings real physical buttons that dynamically appear and disappear into a flat touch screen (see Figure~\ref{tactus}). Small fluid channels are routed throughout the Tactile Layer and enable fluid ot expand the top polymer layer to create the physical buttons \cite{Tactus}.

Although this technology from Tactus is extremely bleeding-edge, it has already received a fair amount of recognition \cite{CNN, I-Zone, PCMag}.

@@

\section{Top-Level Design}
The design aims to assist IBSVI engage their spatial cognition, perception and sensing resources while interacting with touch screens. The tactile stuff is intended to operate in conjunction with other technologies that provide auditory feedback that informs the users of \textit{what} is at the location on the screen while the tactile buttons heps the user know \textit{where} it is. 
\label{background}

>>>>

In this investigation, I propose a ``dream'' interface design for touchscreen mobile devices that provides a significant amount of tactile feedback. This feedback is designed in a way that can be helpful for individuals with and without visual impairments alike. This design was developed with the usability metrics of learnability, efficiency, and error rate in mind.

My ``dream'' interface design makes use of technology that is currently being created by Tactus, a company in Fremont, California \cite{Tactus}. Tactus brings real physical buttons that dynamically appear and disappear into a flat touch screen (see Figure~\ref{tactus}). Small fluid channels are routed throughout the Tactile Layer and enable fluid to expand the top polymer layer to create the physical buttons \cite{Tactus}.

Although this technology from Tactus is extremely bleeding-edge, the prototypes have already received a fair amount of recognition and positive feedback \cite{CNN, I-Zone, PCMag, Wired}. Reviewers articulate how the technology seems to be ``downright magical'' \cite{CNN}. Though the look and feel of Tactus technology is totally futuristic, the technology is supposed to appear in consumer devices early next year \cite{Tactus}. Companies will also be able to customize the panel for different types of buttons, say for example, the buttons on a TV remote. This ``dream'' user interface design makes use of the fact that the possibilities for the panel are varied.

@@

\section{Top-Level Design}
The design of this ``dream'' interface aims to assist users with and without visual impairments alike. The design will use Tactus technology to create a grid-like system for IBSVI so that they can engage their spatial cognition, perception and sensing resources while interacting with touch screens. The design will only enable the grid-like system on-command so to not distract or annoy those who do not benefit from it.

\begin{figure}[ht]
\centering
\includegraphics[width=1in]{wireframe.png} 
\caption{Tactus Technology keyboard}
\label{tactus}
\end{figure}

The tactile stuff is intended to operate in conjunction with other technologies that provide auditory feedback that informs the users of \textit{what} is at the location on the screen while the tactile buttons heps the user know \textit{where} it is. 
\label{background}
